### 2020-07-26 draft.Rmd
Add Tukey HSD as well as Fligner-Policello

```{r}
seed_accounts = treated %>% filter(treatment == 1)
hist(seed_accounts$balchange,
     main="Histogram of balance changes for SEED accounts",
     xlab="Balance Change")

@@

print("Summary statistics for Seed account balance changes")
summary(seed_accounts$balchange)
```

@@

@@

@@

seed_balchange = seed_accounts$balchange
marketing_balchange = (treated %>% filter(marketing==1))$balchange
control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
x = list(control_balchange, marketing_balchange, seed_balchange)
pJCK(x, method="Monte Carlo")

@@

@@

A p-value of 0.0001 means that we reject the null hypothesis in favor of the alternate.

>>>>

```{r}
seed_accounts = treated %>% filter(treatment == 1)
nonseed = treated %>% filter(treatment == 0)
hist(seed_accounts$balchange,
     main="Histogram of balance changes for SEED accounts",
     xlab="Balance Change")

@@

print("Summary statistics for Seed account balance changes")
summary(seed_accounts$balchange)

filtered_nonseeds = nonseed %>% filter(balchange<10000)
hist(nonseed$balchange)
hist(filtered_nonseeds$balchange)

@@

We know very little about the difference in the underlying distributions of the SEED account savings and the non SEED account savings. We can reasonably assuming independence from each other and continuity of both distributions, but not much else. However, the closest test that matches those assumptions is the Fligner-Policello Test.

The Fligner-Policello Test tests for a difference in population median, but it requires both populations to be symmetric. We feel comfortable violating this assumption here for two reasons. One is that once the comparably small number of outliers are removed, the distributions start to become symmetric. The second reason is that this is the most permissive test of center available to us.

We will run this test at a significance level of $\alpha=0.05$ with the following hypothesis.

$H_0: \theta_x = \theta_y$

$H_a: \theta_x < \theta_y$

Where $\theta_x$ represents the true median of the difference in balance changes for the control group and $\theta_y$ represents the true median of the difference in balance changes for SEED accounts.

In addition to testing whether or not the SEED accounts are more effective savings than a control group, we also want to confirm that the SEED accounts are more effective than just the marketing that comes with them. To do this we divide the customers into three groups. A control group, a group that receives marketing but not SEED accounts, and the group with SEED accounts.

Since we have reason to believe that marketing about savings will be more effective than no marketing, and that marketing plus a SEED account will be more effective than just marketing, we will use an ordered k-sample test. Here we use the Jonckheere-Terpstra test as recommended by Higgins. [@Higgins]

We will conduct this test at a significance level of $\alpha=0.05$ with the following hypothesis.

$H_0: \theta_x = \theta_y = \theta_z$

$H_a: \theta_x \leq \theta_y \leq \theta_z$ with at least one strict inequality

Where $\theta_x, \theta_y, \theta_z$ are the medians of the distributions of the savings in the control group, the marketing group, and the SEED accounts respectively.

@@

```{r 2-sample}
x = list(nonseed$balchange, seed_accounts$balchange)
pFligPoli(x, method="Monte Carlo")
```

@@

seed_balchange = seed_accounts$balchange
marketing_balchange = (treated %>% filter(marketing==1))$balchange
control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
x = list(control_balchange, marketing_balchange, seed_balchange)
pJCK(x, method="Monte Carlo")
```

```{r Tukey HSD setup}
# Helper functions
comp_sum = function(val, t1){
# Helper function for Mann-Whitney stat
  full = sum(t1 < val)
  partial = 0.5 * sum(t1 == val)
  return(full+partial)
}

mw_stat = function(t1, t2){
  #Mann-Whitney statistic for two treatments
  comp_sums = mapply(comp_sum, t2, MoreArgs = list(t1=t1))
  return(sum(comp_sums))
}

general_stat_perm= function(full_data, n_s, stat_func){
  # stat_func should take in a list of 
  dataset = list()
  k = length(n_s)
  start=1
  end=0
  for (i in 1:k){
    end = end + n_s[i]
    dataset[[i]] = full_data[start:end]
    start = end + 1
  }
  return(stat_func(dataset))
}

calculate_critical = function(stat_dist, alpha){
  # stat_dist is sorted
  R = length(stat_dist)
  init_crit = stat_dist[R*alpha]
  if(sum(sample_q >= init_crit)/R == alpha){
    return(init_crit)
  }
  index = sum(sample_q > init_crit)
  return(sample_q[index])
}

@@

```{r Tukey HSD}

# Permutation Tukey HSD test
q_star = function(dataset){
  # Permutation HSD pg 97
  # Use the Mann-Whitney for T
  k = length(dataset)
  max_t = 0
  for (i in 1:(k-1)) {
    for(j in (i+1):k){
      t = abs(mw_stat(dataset[[i]], dataset[[j]]))
      if (t > max_t){
        max_t = t
      }
    }
  }
  return(max_t)
}

treat_list = list(
  control=control_balchange,
  marketing=marketing_balchange,
  seed=seed_balchange
)

k = length(treat_list)
n_s = mapply(length, treat_list)
N = sum(n_s)
full_data = unlist(treat_list)

R = 10000
permutations = matrix(NA, ncol = N, nrow=R)
for (i in 1:R){
  permutations[i,] = sample(full_data)
}
sample_q = apply(permutations, 1, general_stat_perm, n_s, q_star)
sample_q = sort(sample_q, decreasing = TRUE)

a_1 = calculate_critical(sample_q, 0.1)
a_05 = calculate_critical(sample_q, 0.05)
crit_message = sprintf("critical values of significance levels 0.1 and 0.05 are %s and %s respectively", a_1, a_05)
print(crit_message)

q_obs = q_star(treat_list)
obs_message = sprintf("The observed value of Q* is: %s", q_obs)
print(obs_message)

counts = sum(sample_q>= q_obs)
p_val = counts/R
p_message = sprintf("With a p-value of %s", p_val)
print(p_message)

```{r}
m = matrix(NA, k, k, 
           dimnames = list(
             names(treat_list),
             names(treat_list)
            )
          )

for (row in names(treat_list)){
  for(col in names(treat_list)){
    m[row,col] = mw_stat(treat_list[[row]], treat_list[[col]])
  }
}
print("pairwise statistics greater than or equal to the 0.05 critical value")
print(m >= a_05)
```

@@

A p-value of 0.0001 for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate. We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.

A p-value of 0.0001 for the Jonckheere-Terpstra test means that we reject the null hypothesis in favor of the alternate. We conclude that there is a difference in savings between the three groups.

A p-value of 0 for the Tukey HSD permutation test shows that the SEED account is awesome. The matrix shows that the SEED accounts had better savings than the control group and the marketing groups. No other differences were significant.
